---
title: "Allele Frequencies by SNP"
author: "Melissa Chapnick"
date: "2022-10-26"
output: html_document
---
## Introduction

The objective of this analysis is to assess whether offspring FADS genotype modifies the impact of prenatal DHA supplementation on global cognitive scores at age 5. 

The data to be analyzed were obtained from the POSGRAD trial.The POSGRAD trial is a double-blind randomized controlled trial conducted in Mexico between 2002-2006 that evaluated the impact of prenatal DHA supplementation on infant anthropometric, health, and cognitive outcomes, and assessed the role of FADS genotypes in modifying the impact of supplementation on these outcomes at birth through 11 years of age. 

The following graphs display allele frequencies by SNP.

```{r}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, include=TRUE)
```


```{r}
#Set filepaths
POSGRADanalyticlocation<-here::here("derived_data/POSGRADdata_merge_analytic.csv")

#Read in data
POSGRADanalytic<-read.csv(POSGRADanalyticlocation,header = TRUE)

```

```{r}
#Examine Allele Frequencies by SNP
library(ggplot2)
library(knitr)
library(dplyr)

#rs174602
ggplot(data=POSGRADanalytic,aes(x=rs174602_o_num))+
  geom_bar(aes(factor(rs174602_o_num)))+
  scale_x_discrete(name="SNP rs174602", labels=c("0"="Homozygote Major","1"= "Heterozygote Major","2"="Homozygote Minor"))+
  ggtitle("FADS 2 SNP rs174602 Allele Frequency ")

kable(POSGRADanalytic%>%
  group_by(rs174602_o_num)%>%
  summarise(n=n())%>%
  mutate(freq=n/sum(n)))

#rs1535
ggplot(data=POSGRADanalytic,aes(x=rs1535_o_num))+
  geom_bar(aes(factor(rs1535_o_num)))+
  scale_x_discrete(name="SNP rs1535", labels=c("0"="Homozygote Major","1"= "Heterozygote Major","2"="Homozygote Minor"))+
  ggtitle("FADS 2 SNP rs1535 Allele Frequency ")

kable(POSGRADanalytic%>%
  group_by(rs1535_o_num)%>%
  summarise(n=n())%>%
  mutate(freq=n/sum(n)))

#rs174448
ggplot(data=POSGRADanalytic,aes(x=rs174448_o_num))+
  geom_bar(aes(factor(rs174448_o_num)))+
  scale_x_discrete(name="SNP rs174448", labels=c("0"="Homozygote Major","1"= "Heterozygote Major","2"="Homozygote Minor"))+
  ggtitle("FADS 2 SNP rs174448 Allele Frequency ")

kable(POSGRADanalytic%>%
  group_by(rs174448_o_num)%>%
  summarise(n=n())%>%
  mutate(freq=n/sum(n)))

#rs174583
ggplot(data=POSGRADanalytic,aes(x=rs174583_o_num))+
  geom_bar(aes(factor(rs174583_o_num)))+
  scale_x_discrete(name="SNP rs174583", labels=c("0"="Homozygote Major","1"= "Heterozygote Major","2"="Homozygote Minor"))+
  ggtitle("FADS 2 SNP rs174583 Allele Frequency ")

kable(POSGRADanalytic%>%
  group_by(rs174583_o_num)%>%
  summarise(n=n())%>%
  mutate(freq=n/sum(n)))

#rs174556 - missing in dataset but of interest!

```


```{r}
#Build table



```

